$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Fixed labels on benchmark plots

\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 

@@

\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}} \\

@@

\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%

>>>>

\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data.png}} 

@@

\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM1_all_tuning_data.png}} \\

@@

\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_fixed_at_ms_BM2_all_tuning_data.png}}%%
